\documentclass[11pt,letterpaper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}

% Page layout
\geometry{
    left=1in,
    right=1in,
    top=1in,
    bottom=1in
}

% Remove page numbers
\pagestyle{empty}

% Sender information
\signature{Pranav Donepudi}
\address{
    Pranav Donepudi \\
    San Diego, CA \\
    donepudipranav04@gmail.com \\
    +1 (650) 759-4788
}

\begin{document}

\begin{letter}{
    Hiring Manager \\
    Snowflake Inc. \\
    Software Engineering Department \\
    [Company Address]
}

\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Software Engineer position at Snowflake, as advertised on your careers page. With over 3 years of experience in designing and building large-scale distributed systems, combined with my passion for data infrastructure and cloud technologies, I am excited about the opportunity to contribute to Snowflake's mission of empowering enterprises through the world's greatest data and applications platform. As a recent graduate with a Master's in Computer Science from Rice University and hands-on experience building production systems at Technogen Inc. and DXC Technology, I am well-prepared to make immediate contributions to your Data Cloud initiatives.

Throughout my career, I have developed a deep appreciation for building end-to-end customer-facing products that solve real business problems. My experience includes designing and implementing scalable backend services, collaborating with cross-functional teams, and driving impactful initiatives that directly improve user experience and system performance. I have worked extensively with Java, Python, and SQL, building production systems that handle significant scale while maintaining high reliability and performance standards.

What particularly excites me about this role is the opportunity to work on Snowflake's Data Cloud platform, specifically in areas such as data sharing, governance, and collaboration. I am drawn to the technical challenges of building secure, governed data sharing mechanisms that enable organizations to unlock the full potential of their data. My strong computer science fundamentals, including deep knowledge of algorithms and data structures, have consistently enabled me to design elegant solutions to complex distributed systems problems.

I am particularly aligned with Snowflake's values of impact, innovation, and collaboration. I thrive in environments where I can both contribute to improving engineering processes and learn from world-class teams. In my current role at Technogen Inc., I architected and deployed end-to-end data workflows for a large-scale application processing over 500 daily transactions, building cloud-native ETL pipelines using Python Flask, AWS SQS, and DynamoDB. Through scalable data models and automation pipelines, I improved system performance by 70\% while maintaining 99.9\% uptime, and developed robust REST APIs that reduced latency by 80\% through comprehensive monitoring and fault tolerance mechanisms. This experience has prepared me to make immediate contributions to Snowflake's engineering initiatives across Apps \& Collaboration, Marketplace, Data Governance, and related areas.

Beyond the core requirements, I bring experience with database internals through my work optimizing genomic data processing systems at Rice University, where I achieved a 67\% improvement in query performance through SQL optimization and efficient schema design. As an AWS Certified Cloud Practitioner with hands-on experience in cloud infrastructure using AWS services (S3, SQS, Lambda, EC2, CloudWatch), Terraform, Docker, and Kubernetes, I understand the importance of building secure, scalable, and governed data platforms. My background in developing automated CI/CD pipelines and implementing comprehensive testing strategies aligns perfectly with Snowflake's commitment to engineering excellence and system reliability.

I am excited about the prospect of joining Snowflake during this period of rapid growth and innovation. I am confident that my technical skills, collaborative mindset, and passion for building impactful products align perfectly with this role. I would welcome the opportunity to discuss how my experience and vision can contribute to Snowflake's continued success.

Thank you for considering my application. I look forward to the opportunity to speak with you further about how I can contribute to building the future of data at Snowflake.

\closing{Sincerely,}

\end{letter}

\end{document}
